Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-09-23 bbbq_article.tex
Mention ClustalOmega and BLOSUM80

To detect the evolutionary conservation of TMHs,
we first selected all unique protein sequences per
gene from all 45k SARS-CoV-2 proteomes,
resulting in around 500 unique protein sequences per gene.
From the unique protein sequences, we made an alignment per gene,
using the msa (\cite{bodenhofer2015msa}) R package, 
using default settings, including the use of the default alignment tool
ClustalW (\cite{thompson1994clustal}).
Instead of the default and general BLOSUM62 amino acid transition matrix (\cite{henikoff1992amino}),
the FLU transition matrix (\cite{dang2010flu}) was used,
as the latter is based on amino acid transitions in another viral pathogen, influenza.
Per alignment, we used msa to determine the consensus sequence
and the conservation scores.
Per consensus sequences, the topology was determined using pureseqtmr.

>>>>

To detect the evolutionary conservation of TMHs,
we first selected all unique protein sequences per
gene from all 45k SARS-CoV-2 proteomes,
resulting in around 500 unique protein sequences per gene.
From the unique protein sequences, we made an alignment per gene,
using the msa (\cite{bodenhofer2015msa}) R package, 
set up to use ClustalOmega (\cite{thompson1994clustal})
with the BLOSUM80 amino acid transition matrix (\cite{henikoff1992amino}).
Per alignment, we used msa to determine the consensus sequence
and the conservation scores.
Per consensus sequences, the topology was determined using pureseqtmr.
